Creating More Meaningful Explanations for Audio Deepfake Detection

### 2025-02-06 draft.tex
expand abstract and change I to we

	I present a method of classification of audio samples as synthetic or bona fide using a
	combination of features with a focus on aspects of a voice sample that can be heard by the
	human ear. I then use this classifier as a surrogate model to produce explanations using the
	LIME method, with the hope of introducing a kind of explainability into this area that has
	the potential to be understood by a wider range of people and not only people who are already
	familiar with the field. I also introduce two metrics in order to evaluate the usefulness of
	the features in the explanations, with the goal of making a conclusion about the potential
	usefulness of explanations generated using this classifier. Experiments were performed using
	the In-the-Wild dataset, a dataset created with a focus on testing generalization of previous
	methods of synthetic audio detection. Several of the surrogate models demonstrated strong
	performance on the dataset, even in comparison to previous methods. However, the explanations
	generated by this method do not seem to offer much potential for useful interpretation using the
	perceptible features, based on an evaluation of aggregated local explanations using the
	proposed metrics, as the imperceptible features have a much larger influence on the
	classification result. I believe, however, that the proposed method offers a promising basis
	for future research into explanations using perceptible features.

@@

	the research discussed in the next section, I would like to use new combinations of features,

@@

		\cite{muller_does_2022}. I have chosen it for these experiments because of the

@@

		useful perspective against which I can compare my method.

@@

			negligible in my experiments. The default threshold is 0.5, meaning that a result

@@

			I approached the second problem by generating intermediate data for the

@@

			user, I pursued the goal of summarizing many explanations generated using the

@@

			standardized metrics for the global evaluation of local metrics, I propose two
			metrics, with which I will make conclusions about the usefulness of this method.

@@

			In order to contextualize the metrics, I will make the following definitions.

@@

			The first metric I will define is the mean of the absolute values of the weights of

@@

			I will further refer to this metric as importance, and it can be mathematically

@@

			The second metric I will define is the average aggregate correctness on a per-feature
			basis, which I will further refer to as trust. The trust per feature can be defined as

@@

	Using the methods described in the previous section, I performed experiments training and

@@

		method, I have used selected two models from the last section and generated explanations
		on the first 500 samples of the testing data. I then summarized the explanations generated

@@

	In this section, I will discuss the implications of the experimental results of the previous

@@

		Because of these models' inclusion of several perceptible features, I made the hypothesis

@@

		the difference was still minimal. In spite of this, I believe that it is still worth

@@

		In spite of the potential that I see with this method, it does also present some

@@

		ones used in my method are able to be heard by the human ear and are even used in

@@

		Finally, I have not addressed in my experiments how the features can be presented to the

@@

	To conclude, I have presented a model architecture using a combination of various features,

@@

	I believe that this is a method that offers a large potential, but is not useful for the
	generation of understandable explanations in its current state. I suggest, however, that this

>>>>

	With the ever-increasing threats posed by fake voice synthesis, reliable detection methods
	have become more important than ever. Previous research has tackled this problem using several
	methods, including various features and model architectures, but there remains a need in the
	area of fake voice detection for a method that offers a kind of explainability that can also
	be understood by the average person. We present a method of classification of audio samples as
	synthetic or bona fide using a combination of features with a focus on aspects of a voice
	sample that can be heard by the human ear, perceptible features. We use this classifier as a
	surrogate model to produce explanations using the LIME method, with the hope of introducing a
	kind of explainability into this area that has the potential to be understood by a wider range
	of people and not only people who are already familiar with the field, in addition to
	introducing two metrics in order to evaluate the contributions of the features to the average
	local explanation through aggregation, with the goal of making a conclusion about the
	potential usefulness of explanations generated using this method to more general audience.
	Experiments were performed using the In-the-Wild dataset, a dataset created with a focus on
	testing generalization of previous methods of synthetic audio detection. Several of the
	surrogate models demonstrated strong performance on the dataset, even in comparison to
	previous methods. However, the explanations generated by this method do not seem to offer much
	potential for useful interpretation using the perceptible features, based on an evaluation of
	aggregated local explanations using the proposed metrics, as the imperceptible features have a
	much larger influence on the classification result. We believe, however, that the proposed
	method offers a promising basis for future research into explanations using perceptible
	features.

@@

	the research discussed in the next section, we would like to use new combinations of features,

@@

		\cite{muller_does_2022}. We have chosen it for these experiments because of the

@@

		useful perspective against which we can compare our method.

@@

			negligible in our experiments. The default threshold is 0.5, meaning that a result

@@

			We approached the second problem by generating intermediate data for the

@@

			user, we pursued the goal of summarizing many explanations generated using the

@@

			standardized metrics for the global evaluation of local metrics, we propose two
			metrics, with which we will make conclusions about the usefulness of this method.

@@

			In order to contextualize the metrics, we will make the following definitions.

@@

			The first metric we will define is the mean of the absolute values of the weights of

@@

			We will further refer to this metric as importance, and it can be mathematically

@@

			The second metric we will define is the average aggregate correctness on a per-feature
			basis, which we will further refer to as trust. The trust per feature can be defined as

@@

	Using the methods described in the previous section, we performed experiments training and

@@

		method, we have used selected two models from the last section and generated explanations
		on the first 500 samples of the testing data. We then summarized the explanations generated

@@

	In this section, we will discuss the implications of the experimental results of the previous

@@

		Because of these models' inclusion of several perceptible features, we made the hypothesis

@@

		the difference was still minimal. In spite of this, we believe that it is still worth

@@

		In spite of the potential that we see with this method, it does also present some

@@

		ones used in our method are able to be heard by the human ear and are even used in

@@

		Finally, we have not addressed in our experiments how the features can be presented to the

@@

	To conclude, we have presented a model architecture using a combination of various features,

@@

	We believe that this is a method that offers a large potential, but is not useful for the
	generation of understandable explanations in its current state. We suggest, however, that this
